A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-08 paper.tex
Add the remote PoW figure and description of RPi3

\subsubsection{Messages Publishment}
Publishing a message to MAM is attaching a zero-value transaction to the Tangle which requires two processes:
\begin{itemize}
	\item	Tips selection: In the IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify. The tips are provided by IOTA full nodes.
	\item	Proof-of-Work (PoW): An algorithm which prevents Denial of Service and spam attacks on a network. A computationally hard puzzle to solve, but easy to verify. IOTA uses a Hashcash\cite{Hashcash} based puzzle.
\end{itemize}

Tips selection requires a stable network connection to wait the response from IOTA full nodes, and PoW requires enough computation resources to perform. Fig.~\ref{fig:mam_send} shows probability distribution function of publishing a message to MAM endpoint. The time of Raspberry Pi 3 distributed widely, since the randomness of PoW has huge impact while all the tests on PC remain in a possible range.

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{mam_send}
    \caption{Time cost of sending a message through MAM.}
    \label{fig:mam_send}
\end{figure}

@@

Therefore, transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework. Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator\cite{TA}. Where Ethereum client is used to interact with Ethereum and Tangle-accelerator is a caching proxy server for IOTA, which can serve thousands of IOTA requests at once without accessing remote IOTA full nodes frequently and provide PoW acceleration. However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.

>>>>

\subsubsection{Messages Publishment}
Publishing a message to MAM is attaching a zero-value transaction to the Tangle which requires two processes:
\begin{itemize}
	\item	Tips selection: In the IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify. The tips are provided by IOTA full nodes.
	\item	Proof-of-Work (PoW): An algorithm which prevents Denial of Service and spam attacks on a network. A computationally hard puzzle to solve, but easy to verify.
\end{itemize}

Tips selection requires a stable network connection to wait the response from IOTA full nodes, and PoW requires enough computation resources to perform. Fig.~\ref{fig:mam_send} shows probability distribution function of publishing a message to MAM endpoint. The time of Raspberry Pi 3 distributed widely, since the randomness of PoW has huge impact while all the tests on PC remain in a acceptable range.

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{mam_send}
    \caption{The probability distributed function of time cost for sending a message through MAM.}
    \label{fig:mam_send}
\end{figure}

@@

Therefore, transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework. Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation. Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with local Pow on Raspberry Pi 3 and remote Pow on Tangle-accelerator. However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{rpi3_pow}
    \caption{Local PoW vs. Remote PoW}
    \label{fig:rpi3_pow}
\end{figure}
